Supermassive black holes and their host spheroids \\ III. Mbh-n paper

### 2015-11-11 papers/mbhn/mbhn.tex
wed

\shorttitle{Mbh-n paper}
\shortauthors{Savorgnan \& Graham}

@@

\author{G. A. D. Savorgnan\altaffilmark{1} and A. W. Graham\altaffilmark{1}}
\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
\email{gsavorgn@astro.swin.edu.au}

\begin{abstract}
blah blah
\end{abstract}

@@

\begin{equation}

@@

\end{equation}

@@

After \cite{graham2001} showed that the black hole mass is tightly linked to the stellar light concentration of spheroids 

@@

\section{Analysis and results}
\label{sec:anal}
As in \emph{Paper II}, a linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ 
(Table \ref{tab:lregLn} and Figure \ref{fig:magn})
and $M_{\rm BH} - n_{\rm sph}$ (Table \ref{tab:lregMn} and Figure \ref{fig:mbhn}) diagrams 
was performed using three different routines: 
the BCES code from \cite{akritasbershady1996}, 
the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}.
All of these three routines take into account the intrinsic scatter, 
but only the FITEXY and the {\tt linmix\_err} codes allow one to quantify it.
We report both symmetrical and nonsymmetrical linear regressions.  
Symmetrical regressions are meant to be compared with theoretical expectations, 
whereas nonsymmetrical forward ($Y|X$) regressions -- which minimize the scatter in the $Y$ direction -- 
allow one to predict the value of the observable $Y$ with the best possible precision. \\
We searched for extreme outliers in both the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams, 
and found that in our $L_{\rm sph} - n_{\rm sph}$ plot there are no $3\sigma$ outliers, 
whereas in our $M_{\rm BH} - n_{\rm sph}$ plot 
the S0 galaxies NGC 0524 and NGC 3998 reside more than $3\sigma$ from the bisector linear regression for all galaxies. 
These two galaxies have therefore been excluded from the rest of the analysis. {\bf mergers are excluded?? 62??} \\
{\bf fitexy does better job, we report that} \\

\subsection{$L_{\rm sph} - n_{\rm sph}$}
Following \cite{graham2001}, 
who showed that the $L_{\rm sph} - n_{\rm sph}$ relation is different for elliptical galaxies and the bulges of disk galaxies (S0+Sp), 
\cite{savorgnan2013} re-analyzed the data from \cite{grahamguzman2003} and \cite{graham2013review} 
and obtained two separate $L_{\rm sph} - n_{\rm sph}$ linear regressions for elliptical galaxies and the bulges of disk galaxies 
(in the B- and K-band, respectively). 
At the time, the $L_{\rm sph} - n_{\rm sph}$ datasets from \cite{grahamguzman2003} and \cite{graham2013review} were of the best quality available 
to investigate the $L_{\rm sph} - n_{\rm sph}$ relation for different galaxy morphological types. 
However, these datasets were not obtained from a homogeneous analysis, 
but they were a collection of results taken from various past bulge/disk decomposition studies. 
It is also worth mentioning that, 
although the K-band luminosities of the bulges of disk galaxies had been corrected for internal dust absorption, 
{\bf the dust corrections are not precise today refs??, imagine at the time.....}  
Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram with our high-quality dataset  
derived from state-of-the-art multicomponent decompositions, 
that were performed in a consistent manner 
and using the $3.6\rm~\mu m$ band, which is less affected by dust extinction than the K-band. \\
\cite{graham2013review} presented a single $L_{\rm sph} - n_{\rm sph}$ correlation for the bulges of disk galaxies (S0+Sp).
However, using our dataset, 
we fit the $L_{\rm sph} - n_{\rm sph}$ relation for elliptical, lenticular and spiral galaxies separately, 
and found that the values of the slope and intercept for the lenticular galaxies 
are not consistent within the errors with those for the spiral galaxies, 
but are consistent within the errors with those for the elliptical galaxies.  
Given this, we conclude that in the $L_{\rm sph} - n_{\rm sph}$ diagram 
elliptical and lenticular galaxies form together a single (\emph{early-type}) sequence, 
whereas the combination of lenticular and spiral galaxies do not. 
{\bf why?? dust? multicomponent? classification?}

@@

\subsection{$M_{\rm BH} - n_{\rm sph}$}
\cite{grahamscott2013} presented two different $M_{\rm BH} - L_{\rm sph}$ relations for S\'ersic and core-S\'ersic 
spheroids\footnote{Core-S\'ersic spheroids have partially depleted cores relative to their outer S\'ersic light profile, 
whereas S\'ersic spheroids have no central deficit of stars. } \citep{graham2003coresersicmodel,trujillo2004coresersicmodel}.
However, in \emph{Paper II} we found that the slopes of the $M_{\rm BH} - L_{\rm sph}$ correlations for S\'ersic and core-S\'ersic spheroids 
are consistent with each other within their $1\sigma$ uncertainties, 
which prevents us from considering them as two separate sequences. 
On the other hand, our analysis showed that early- and late-type galaxies follow two different $M_{\rm BH} - L_{\rm sph}$ relations 
($M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ 
and $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$, respectively). \\
Given that early- and late-type galaxies define two separate sequences in both the $L_{\rm sph} - n_{\rm sph}$ 
and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
we investigate substructure in the $M_{\rm BH} - n_{\rm sph}$ diagram. 
Using the results from the modified FITEXY routine, 
we find that 
early-type galaxies follow $M_{\rm BH} \propto n_{\rm sph}^{3.58 \pm 0.27}$, 
while late-type galaxies follow $M_{\rm BH} \propto n_{\rm sph}^{4.55 \pm 0.66}$. 
The Bayesian estimator {\tt linmix\_err} returns consistent results: 
a slope of $3.44 \pm 0.33$ for the early-type galaxies 
and a slope of $4.12 \pm 1.07$ for the late-type galaxies. 
In both cases, the values of the slope and intercept for the early- and late-type galaxies 
are consistent with each other within their $1\sigma$ uncertainties\footnote{In effect, 
considering the results of the modified FITEXY routine, 
the slopes of the relations for early- and late-type galaxies 
are only marginally consistent with each other within their $1\sigma$ uncertainties. 
However, the same slopes obtained with Bayesian estimator {\tt linmix\_err} 
are fully consistent with each other within their $1\sigma$ uncertainties. }.
Our analysis shows that the early- and late-type galaxies do not follow two separate trends in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
i.e.~we do not identify any significant substructure based on the galaxy morphological type. \\
The symmetrical linear regression for all galaxies obtained with the modified FITEXY routine is: 
\begin{equation}
\log \biggl( \frac{M_{\rm BH}}{\rm M_\odot} \biggr) = (8.18 \pm 0.06) + (3.39 \pm 0.15) \bigl(\log n_{\rm sph}^{\rm maj} - 0.51 \bigr) .
\end{equation}

@@

\section{Discussion and conclusions} 
We have seen that the early- and late-type galaxies in the $M_{\rm BH} - n_{\rm sph}$ diagram can be fit with a single power-law, 
whereas they follow two separate correlations in the $M_{\rm BH} - L_{\rm sph}$ diagram (\emph{Paper II}). 
We now want to compare the amount of scatter among these two plots. 
When considering all galaxies, irrespective of their morphological type, 
the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is smaller than that of the $M_{\rm BH} - L_{\rm sph}$ relation. 
However, because of the different nature of the $M_{\rm BH} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ correlations 
(single and double power-law, respectively),  
we are not comparing apples with apples. 
One can obtain more informative results by considering early- and late-type galaxies separately. 
For early-type galaxies only, the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is consistent\footnote{Looking 
at the results obtained with the modified FITEXY routine, 
the values of the intrisic scatter are only marginally consistent with each other, 
but looking at the results obtained with the Bayesian estimator {\tt linmix\_err}, 
the values of the intrisic scatter are fully consistent with each other. } with  
that of the $M_{\rm BH} - L_{\rm sph}$ relation (within their $1\sigma$ uncertainties). 
For late-type galaxies only, the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is consistent with 
that of the $M_{\rm BH} - L_{\rm sph}$ relation, 
{\bf except fitexy xy}.

data suggest that m-n more fundamental than l-n or m-l woooooh? \\

\begin{table*}
\centering
\caption{Linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph}^{\rm maj} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
 & \multicolumn{6}{l}{$MAG_{\rm sph}/{\rm [mag]} = \alpha + \beta \bigl(\log n_{\rm sph}^{\rm maj} - \langle \log n_{\rm sph}^{\rm maj} \rangle \bigr)$} \\ [0.5em]
All (62)               & BCES $(Y|X)$               & $-23.88 \pm 0.15$ & $-7.17 \pm 0.80$ & $0.51$ & $-$ & $1.18$ \\
                       & mFITEXY $(Y|X)$            & $-23.95 \pm 0.13$ & $-6.70 \pm 0.45$ & $0.51$ & $0.56^{+0.15}_{-0.10}$ & $0.98$ \\
                       & {\tt linmix\_err} $(Y|X)$  & $-23.92 \pm 0.15$ & $-6.40 \pm 0.57$ & $0.51$ & $0.74 \pm 0.13$ & $1.07$ \\ [0.5em]
                       & BCES $(X|Y)$               & $-23.88 \pm 0.14$ & $-6.70 \pm 0.51$ & $0.51$ & $-$ & $1.11$ \\
                       & mFITEXY $(X|Y)$            & $-23.94 \pm 0.14$ & $-7.50 \pm 0.52$ & $0.51$ & $0.59^{+0.17}_{-0.11}$ & $1.23$ \\
                       & {\tt linmix\_err} $(X|Y)$  & $-23.94 \pm 0.16$ & $-7.51 \pm 0.62$ & $0.51$ & $0.81 \pm 0.16$ & $1.23$ \\ [0.5em]
                       & BCES Bisector              & $-23.88 \pm 0.14$ & $-6.93 \pm 0.60$ & $0.51$ & $-$ & $1.14$ \\
                       & mFITEXY Bisector           & $-23.94 \pm 0.13$ & $-7.08 \pm 0.34$ & $0.51$ & $-$ & $1.16$ \\
                       & {\tt linmix\_err} Bisector & $-23.93 \pm 0.16$ & $-6.91 \pm 0.42$ & $0.51$ & $-$ & $1.14$ \\ [0.5em]

@@

\tableline 
\tableline
\end{tabular}
\label{tab:lregLn} 
\tablecomments{For each subsample, we indicate $\langle \log n_{\rm sph} \rangle$, its average value of spheroid S\'ersic index. 
In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $L_{\rm sph}$ direction. 
all - mergers - outliers
Both the early- and late-type subsamples do not contain the two galaxies classified as S0/Sp and the two galaxies classified as mergers (45+17=66-2-2). }
\end{table*}

\begin{table*}
\centering
\caption{Linear regression analysis of the $M_{\rm BH} - n_{\rm sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph}^{\rm maj} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
 & \multicolumn{6}{l}{$\log \bigl( M_{\rm BH}/{\rm [M_\odot]} \bigr) = \alpha + \beta \bigl(\log n_{\rm sph}^{\rm maj} - \langle \log n_{\rm sph}^{\rm maj} \rangle \bigr)$} \\ [0.5em]
 All (62)		& BCES $(Y|X)$  	     & $8.14 \pm 0.08$ & $3.56 \pm 0.38$ & $0.51$ & $-$ & $0.60$ \\
 			& mFITEXY $(Y|X)$	     & $8.18 \pm 0.06$ & $3.27 \pm 0.21$ & $0.51$ & $0.22^{+0.10}_{-0.07}$ & $0.45$ \\
 			& {\tt linmix\_err} $(Y|X)$  & $8.17 \pm 0.06$ & $3.17 \pm 0.24$ & $0.51$ & $0.29 \pm 0.07$ & $0.56$ \\ [0.5em]
 			& BCES $(X|Y)$  	     & $8.14 \pm 0.08$ & $3.56 \pm 0.25$ & $0.51$ & $-$ & $0.60$ \\
 			& mFITEXY $(X|Y)$	     & $8.18 \pm 0.06$ & $3.51 \pm 0.23$ & $0.51$ & $0.23^{+0.10}_{-0.07}$ & $0.60$ \\
 			& {\tt linmix\_err} $(X|Y)$  & $8.17 \pm 0.07$ & $3.49 \pm 0.26$ & $0.51$ & $0.30 \pm 0.07$ & $0.60$ \\ [0.5em]
 			& BCES Bisector 	     & $8.14 \pm 0.08$ & $3.56 \pm 0.29$ & $0.51$ & $-$ & $0.60$ \\
 			& mFITEXY Bisector	     & $8.18 \pm 0.06$ & $3.39 \pm 0.15$ & $0.51$ & $-$ & $0.58$ \\
 			& {\tt linmix\_err} Bisector & $8.17 \pm 0.07$ & $3.33 \pm 0.18$ & $0.51$ & $-$ & $0.57$ \\ [0.5em]

@@

\tableline 
\tableline
\end{tabular}
\label{tab:lregMn} 
\tablecomments{For each subsample, we indicate $\langle \log n_{\rm sph} \rangle$, its average value of spheroid S\'ersic index. 
In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $L_{\rm sph}$ direction. 
all - mergers - outliers
Both the early- and late-type subsamples do not contain the two galaxies classified as S0/Sp and the two galaxies classified as mergers (45+17=66-2-2).  }
\end{table*}

  \begin{table*}
  \centering
  \caption{Intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ relations.}
  \begin{tabular}{llccr}
  \tableline
  \tableline
  {\bf Subsample} & {\bf Regression} & $\boldsymbol \epsilon$ {\bf for} $\boldsymbol M_{\rm BH} - n_{\rm sph}$ & 
  $\boldsymbol \epsilon$ {\bf for} $\boldsymbol M_{\rm BH} - L_{\rm sph}$ & \\ 
  \tableline 
  \\
  All		  & mFITEXY $(Y|X)$	      & $0.22^{+0.10}_{-0.07}$ & $0.49^{+0.06}_{-0.05}$ & non consist. \\
 		  & {\tt linmix\_err} $(Y|X)$ & $0.29 \pm 0.07$ & $0.51 \pm 0.06$               & non consist. \\
 		  & mFITEXY $(X|Y)$	      & $0.23^{+0.10}_{-0.07}$ & $0.58^{+0.07}_{-0.06}$ & non consist. \\
 		  & {\tt linmix\_err} $(X|Y)$ & $0.30 \pm 0.07$ & $0.60 \pm 0.09$               & non consist. \\ [0.5em]

>>>>

\shorttitle{Mbh-n paper}
\shortauthors{Savorgnan}

@@

\author{G. A. D. Savorgnan\altaffilmark{1}}
\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
\email{gsavorgn@astro.swin.edu.au}

\begin{abstract}
The S\'ersic $R^{1/n}$ model is the best approximation known to date for describing the light distribution of stellar spheroidal and disk components, 
with the S\'ersic index $n$ providing a direct measure of the central radial concentration of stars. 
The S\'ersic index of a galaxy's spheroidal component $n_{\rm sph}$ has been shown to tightly correlate 
with the mass of the central supermassive black hole $M_{\rm BH}$ by some studies. 
The $M_{\rm BH} - n_{\rm sph}$ correlation is also expected from other two well known galaxy scaling relations: 
the $L_{\rm sph} - n_{\rm sph}$ and the $M_{\rm BH} - L_{\rm sph}$ relations, 
where $L_{\rm sph}$ indicates the galaxy's spheroid luminosity. 
However, it is widely recognized that obtaining an accurate estimate of the spheroid S\'ersic index is a challenging task, 
and -- not surprisingly -- other studies have failed to recover a statistically significant $M_{\rm BH} - n_{\rm sph}$ correlation. 
With the aim of re-investigating the $M_{\rm BH} - n_{\rm sph}$ 
and other correlations between the black hole mass and various galaxy properties, 
we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, etc.) 
decomposition of 66 galaxies, with directly measured black hole masses, 
that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}. 
This sample is the largest to date used to investigate black hole mass scaling relations. 
In this paper, the third of its series, we present an analysis of the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams. 
While early-type (elliptical+lenticular) and late-type (spiral) galaxies split into two separate relations 
in the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
they reunite in a single $M_{\rm BH} \propto n_{\rm sph}^{3.39 \pm 0.15}$ sequence
with relatively small intrinsic scatter ($\epsilon_{(Y|X)} \simeq 0.25 \rm~dex$). 
{\bf to be finished...}
\end{abstract}

@@

\begin{equation*}

@@

\end{equation*}

@@

After \cite{graham2001bulges} showed that the black hole mass is tightly linked to the stellar light concentration of spheroids 

@@

\section{Analysis and results}
\label{sec:anal}
As in \emph{Paper II}, a linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ 
(Table \ref{tab:lregLn} and Figure \ref{fig:magn})
and $M_{\rm BH} - n_{\rm sph}$ (Table \ref{tab:lregMn} and Figure \ref{fig:mbhn}) diagrams 
was performed using three different routines: 
the BCES code from \cite{akritasbershady1996}, 
the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}.
All of these three routines take into account the intrinsic scatter, 
but only the FITEXY and the {\tt linmix\_err} codes allow one to quantify it.
We report both symmetrical and nonsymmetrical linear regressions.  
Symmetrical regressions are meant to be compared with theoretical expectations, 
whereas nonsymmetrical forward ($Y|X$) regressions -- which minimize the scatter in the $Y$ direction -- 
allow one to predict the value of the observable $Y$ with the best possible precision. \\
We searched for extreme outliers in both the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams, 
and found that in our $L_{\rm sph} - n_{\rm sph}$ plot there are no $3\sigma$ outliers, 
whereas in our $M_{\rm BH} - n_{\rm sph}$ plot 
the S0 galaxies NGC 0524 and NGC 3998 reside more than $3\sigma$ from the bisector linear regression for all galaxies. 
These two galaxies have therefore been excluded from the rest of the analysis.

\subsection{$L_{\rm sph} - n_{\rm sph}$}
Following \cite{graham2001}, 
who showed that the $L_{\rm sph} - n_{\rm sph}$ relation is different for elliptical galaxies and the bulges of disk galaxies (S0+Sp), 
\cite{savorgnan2013} re-analyzed the data from \cite{grahamguzman2003} and \cite{graham2013review} 
and obtained two separate $L_{\rm sph} - n_{\rm sph}$ linear regressions for elliptical galaxies and the bulges of disk galaxies 
(in the B- and K-band, respectively). 
At the time, the $L_{\rm sph} - n_{\rm sph}$ datasets from \cite{grahamguzman2003} and \cite{graham2013review} were of the best quality available 
to investigate the $L_{\rm sph} - n_{\rm sph}$ relation for different galaxy morphological types. 
However, these datasets were not obtained from a homogeneous analysis, 
but they were a collection of results taken from various past bulge/disk decomposition studies. 
It is also worth mentioning that, 
although the K-band luminosities of the bulges of disk galaxies had been corrected for internal dust absorption, 
{\bf such corrections are still not very accurate today?!? Driver et al. xxxx??? }  
Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram with our high-quality dataset  
derived from state-of-the-art multicomponent decompositions, 
that were performed in a consistent manner 
and using the $3.6\rm~\mu m$ band, which is less affected by dust extinction than the K-band. \\
\cite{graham2013review} presented a single $L_{\rm sph} - n_{\rm sph}$ correlation for the bulges of disk galaxies (S0+Sp).
However, using our dataset, 
we fit the $L_{\rm sph} - n_{\rm sph}$ relation for elliptical, lenticular and spiral galaxies separately, 
and found that the values of the slope and intercept for the lenticular galaxies 
are not consistent within the errors with those for the spiral galaxies, 
but are consistent within the errors with those for the elliptical galaxies.  
Given this, we conclude that in the $L_{\rm sph} - n_{\rm sph}$ diagram 
elliptical and lenticular galaxies form together a single (\emph{early-type}) sequence, 
whereas the combination of lenticular and spiral galaxies do not. 
{\bf why?? dust? multicomponent? classification?}

@@

\subsection{$M_{\rm BH} - n_{\rm sph}$}
\cite{grahamscott2013} presented two different $M_{\rm BH} - L_{\rm sph}$ relations for S\'ersic and core-S\'ersic 
spheroids\footnote{Core-S\'ersic spheroids have partially depleted cores relative to their outer S\'ersic light profile, 
whereas S\'ersic spheroids have no central deficit of stars. } \citep{graham2003coresersicmodel,trujillo2004coresersicmodel}.
However, in \emph{Paper II} we found that the slopes of the $M_{\rm BH} - L_{\rm sph}$ correlations for S\'ersic and core-S\'ersic spheroids 
are consistent with each other within their $1\sigma$ uncertainties, 
which prevents us from considering them as two separate sequences. 
On the other hand, our analysis showed that early- and late-type galaxies follow two different $M_{\rm BH} - L_{\rm sph}$ relations 
($M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ 
and $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$, respectively). \\
Given that early- and late-type galaxies define two separate sequences in both the $L_{\rm sph} - n_{\rm sph}$ 
and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
we investigate substructure in the $M_{\rm BH} - n_{\rm sph}$ diagram. 
Using the results from the modified FITEXY routine, 
we find that 
early-type galaxies follow $M_{\rm BH} \propto n_{\rm sph}^{3.58 \pm 0.27}$, 
while late-type galaxies follow $M_{\rm BH} \propto n_{\rm sph}^{4.55 \pm 0.66}$. 
The Bayesian estimator {\tt linmix\_err} returns consistent results: 
a slope of $3.44 \pm 0.33$ for the early-type galaxies 
and a slope of $4.12 \pm 1.07$ for the late-type galaxies. 
In both cases, the values of the slope and intercept for the early- and late-type galaxies 
are consistent with each other within their $1\sigma$ uncertainties\footnote{In effect, 
considering the results of the modified FITEXY routine, 
the slopes of the relations for early- and late-type galaxies 
are only marginally consistent with each other within their $1\sigma$ uncertainties. 
However, the same slopes obtained with Bayesian estimator {\tt linmix\_err} 
are fully consistent with each other within their $1\sigma$ uncertainties. }.
Our analysis shows that the early- and late-type galaxies do not follow two separate trends in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
i.e.~we do not identify any significant substructure based on the galaxy morphological type. \\
The symmetrical linear regression for all galaxies obtained with the modified FITEXY routine is: 
\begin{equation*}
\log \biggl( \frac{M_{\rm BH}}{\rm M_\odot} \biggr) = (8.15 \pm 0.06) + (3.37 \pm 0.15) \bigl(\log n_{\rm sph}^{\rm maj} - 0.50 \bigr) . 
\end{equation*}
\\

We have seen that the early- and late-type galaxies in the $M_{\rm BH} - n_{\rm sph}$ diagram can be fit with a single power-law, 
whereas they follow two separate correlations in the $M_{\rm BH} - L_{\rm sph}$ diagram (\emph{Paper II}). 
We now want to compare the amount of scatter among these two plots. 
In Table \ref{tab:intsc} we summarize the values of the intrinsic scatter 
in the $M_{\rm BH} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ diagrams 
for all, early- and late-type galaxies, 
obtained with the modified FITEXY routine and the Bayesian estimator {\tt linmix\_err}. 
When considering all galaxies, irrespective of their morphological type, 
the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is smaller than that of the $M_{\rm BH} - L_{\rm sph}$ relation. 
However, this is obviously not a fair comparison, 
because of the different nature of the $M_{\rm BH} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ correlations 
(single and double power-law, respectively). 
One can obtain more informative results by considering early- and late-type galaxies separately. 
For the early-type galaxies, the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is consistent\footnote{Looking 
at the results obtained with the modified FITEXY routine, 
the values of the intrisic scatter are only marginally consistent with each other, 
but looking at the results obtained with the Bayesian estimator {\tt linmix\_err}, 
the values of the intrisic scatter are fully consistent with each other. } 
with that of the $M_{\rm BH} - L_{\rm sph}$ relation (within their $1\sigma$ uncertainties). 
For the late-type galaxies, the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is consistent with 
that of the $M_{\rm BH} - L_{\rm sph}$ relation, 
except for the inverse ($X|Y$) regression obtained with the modified FITEXY routine. \\
In passing, we note that the values of the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation 
are systematically smaller -- although consistent within the errors -- 
than the corresponding values of the intrinsic scatter of the $M_{\rm BH} - L_{\rm sph}$ relation. 
In addition, the values of the intrinsic scatter returned by the modified FITEXY routine are systematically smaller than 
those output by the Bayesian estimator {\tt linmix\_err}.

@@

\section{Conclusions}

\begin{table*}
\centering
\caption{Linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph}^{\rm maj} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
 & \multicolumn{6}{l}{$MAG_{\rm sph}/{\rm [mag]} = \alpha + \beta \bigl(\log n_{\rm sph}^{\rm maj} - \langle \log n_{\rm sph}^{\rm maj} \rangle \bigr)$} \\ [0.5em]
All (64)               & BCES $(Y|X)$               & $-23.89 \pm 0.15$ & $-6.90 \pm 0.74$ & $0.50$ & $-$ & $1.22$ \\
                       & mFITEXY $(Y|X)$            & $-23.91 \pm 0.13$ & $-6.63 \pm 0.45$ & $0.50$ & $0.59^{+0.16}_{-0.11}$ & $1.01$ \\
                       & {\tt linmix\_err} $(Y|X)$  & $-23.89 \pm 0.14$ & $-6.34 \pm 0.57$ & $0.50$ & $0.74 \pm 0.13$ & $1.14$ \\ [0.5em]
                       & BCES $(X|Y)$               & $-23.89 \pm 0.15$ & $-6.75 \pm 0.52$ & $0.50$ & $-$ & $1.20$ \\
                       & mFITEXY $(X|Y)$            & $-23.89 \pm 0.14$ & $-7.49 \pm 0.53$ & $0.50$ & $0.62^{+0.18}_{-0.12}$ & $1.32$ \\
                       & {\tt linmix\_err} $(X|Y)$  & $-23.90 \pm 0.16$ & $-7.49 \pm 0.62$ & $0.50$ & $0.80 \pm 0.16$ & $1.32$ \\ [0.5em]
                       & BCES Bisector              & $-23.89 \pm 0.15$ & $-6.83 \pm 0.58$ & $0.50$ & $-$ & $1.21$ \\
                       & mFITEXY Bisector           & $-23.90 \pm 0.13$ & $-7.04 \pm 0.35$ & $0.50$ & $-$ & $1.24$ \\
                       & {\tt linmix\_err} Bisector & $-23.89 \pm 0.15$ & $-6.87 \pm 0.42$ & $0.50$ & $-$ & $1.21$ \\ [0.5em]

@@

\tableline 
\tableline
\end{tabular}
\label{tab:lregLn} 
\tablecomments{For each subsample, we indicate $\langle \log n_{\rm sph} \rangle$, its average value of spheroid S\'ersic index. 
In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $L_{\rm sph}$ direction. 
The lenticular galaxies NGC 0524 and NGC 3998 were excluded from the linear regression analysis (see Section \ref{sec:anal}). 
Both the early- and late-type subsamples do not contain the two galaxies classified as S0/Sp and the two galaxies classified as mergers (45+17=66-2-2). }
\end{table*}

\begin{table*}
\centering
\caption{Linear regression analysis of the $M_{\rm BH} - n_{\rm sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph}^{\rm maj} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
 & \multicolumn{6}{l}{$\log \bigl( M_{\rm BH}/{\rm [M_\odot]} \bigr) = \alpha + \beta \bigl(\log n_{\rm sph}^{\rm maj} - \langle \log n_{\rm sph}^{\rm maj} \rangle \bigr)$} \\ [0.5em]
 All (64)		& BCES $(Y|X)$  	     & $8.14 \pm 0.07$ & $3.49 \pm 0.36$ & $0.50$ & $-$ & $0.61$ \\
 			& mFITEXY $(Y|X)$	     & $8.15 \pm 0.06$ & $3.26 \pm 0.21$ & $0.50$ & $0.22^{+0.10}_{-0.07}$ & $0.46$ \\
 			& {\tt linmix\_err} $(Y|X)$  & $8.15 \pm 0.06$ & $3.17 \pm 0.24$ & $0.50$ & $0.28 \pm 0.07$ & $0.56$ \\ [0.5em]
 			& BCES $(X|Y)$  	     & $8.14 \pm 0.08$ & $3.52 \pm 0.25$ & $0.50$ & $-$ & $0.61$ \\
 			& mFITEXY $(X|Y)$	     & $8.15 \pm 0.06$ & $3.49 \pm 0.23$ & $0.50$ & $0.23^{+0.10}_{-0.07}$ & $0.61$ \\
 			& {\tt linmix\_err} $(X|Y)$  & $8.15 \pm 0.07$ & $3.49 \pm 0.26$ & $0.50$ & $0.29 \pm 0.08$ & $0.61$ \\ [0.5em]
 			& BCES Bisector 	     & $8.14 \pm 0.07$ & $3.51 \pm 0.28$ & $0.50$ & $-$ & $0.61$ \\
 			& mFITEXY Bisector	     & $8.15 \pm 0.06$ & $3.37 \pm 0.15$ & $0.50$ & $-$ & $0.59$ \\
 			& {\tt linmix\_err} Bisector & $8.15 \pm 0.07$ & $3.32 \pm 0.18$ & $0.50$ & $-$ & $0.58$ \\ [0.5em]

@@

\tableline 
\tableline
\end{tabular}
\label{tab:lregMn} 
\tablecomments{For each subsample, we indicate $\langle \log n_{\rm sph} \rangle$, its average value of spheroid S\'ersic index. 
In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $L_{\rm sph}$ direction. 
The lenticular galaxies NGC 0524 and NGC 3998 were excluded from the linear regression analysis (see Section \ref{sec:anal}). 
Both the early- and late-type subsamples do not contain the two galaxies classified as S0/Sp and the two galaxies classified as mergers (45+17=66-2-2).  }
\end{table*}
